Viscous Erosion in Porous Media

### 2018-02-26 docs/methods/erosion_methods.tex
NM

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: We run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{l l l l}
\hline
\hspace{0.0pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order
\hspace{0.5pc} & CPU time \\
\hline
%
1/50		& 1.68E-5		& --		& 55 secs		\\
1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
1/200	& 1.30E-6		& 1.90	& 3.5 mins		\\
1/400	& 3.36E-7		& 1.95	& 7.2 mins		\\
1/800	& 8.54E-8		& 1.98	& 15 mins		\\
1/1600	& 2.15E-8		& 1.99	& 30 mins (?)	\\
1/3200	& 5.40E-9		& 1.99	& 60 mins (?)	\\
1/6400	& --			& --		& 2.0 hours(?)	\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0

>>>>

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: We run single-body erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$-difference in shapes obtained with successive temporal resolutions. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{l l l l}
\hline
\hspace{0.0pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order
\hspace{0.5pc} & CPU time \\
\hline
%
1/50		& 1.68E-5		& --		& 55 secs		\\
1/100	& 4.84E-6		& 1.79	& 1.8 mins		\\
1/200	& 1.30E-6		& 1.90	& 3.5 mins		\\
1/400	& 3.36E-7		& 1.95	& 7.2 mins		\\
1/800	& 8.54E-8		& 1.98	& 15 mins		\\
1/1600	& 2.15E-8		& 1.99	& 30 mins (?)	\\
1/3200	& 5.40E-9		& 1.99	& 60 mins (?)	\\
1/6400	& --			& --		& 2.0 hours(?)	\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0
